\begin{doublespace}
\begin{tightcenter}
PUBLIC ABSTRACT
\mylinespacing
\end{tightcenter}

Prior to your first thesis deposit, replace this text with the text of your public abstract. The text of this abstract should be double spaced and each new paragraph should be indented. The text may be altered between first and final deposits. This abstract is required for all thesis/dissertations. 

The public abstract is to be placed at this point in your first and final deposit and submitted via webform at final deposit. This abstract may be up to 250 words and should be written for a non-academic lay audience. In writing your public abstract, avoid jargon and technical language as much as possible. 

The ability to communicate research simply and clearly is an important skill when interviewing for faculty positions, as well as for positions in industry and alt-ac sectors. The public abstract helps convey ideas beyond one’s immediate academic circle, facilitating communication with colleagues who do different kinds of work and possess different dimensions of training.

Think of your public abstract as your “elevator pitch” or what you might tell someone who asks, “What is your thesis about?” You may only have a few minutes to explain it to them while keeping their attention and using terminology you are sure they will understand without further lengthy explanation.

Another way to think of your public abstract is like the description you would read on the inside of a book cover.

\end{doublespace}
